A Physically Motivated Framework to Compare Merger Timescales\\ of Isolated Low- and High-Mass Galaxy Pairs Across Cosmic Time

### 2024-03-26 paper/main.tex
Updates from Overleaf

\section{Pair Sample Properties}
\begin{figure}[htb]
    \begin{center}
    \includegraphics[width=\columnwidth]{plots/bet-on-it/6_paircount.png}
    \caption{The number of low-mass (green) and high-mass (pink) unique pairs (or distinct orbits) that are post-infall and pre-merger as a function of redshift. 
    The solid lines show the total number of pairs at a given redshift (including non-mergers and mergers that have yet to merge), while dashed lines show the number of post-infall orbits at a given redshift that will merge before $z=0$.
    We only count the number of orbits ``at" a given redshift if they have not merged, but have experienced first infall at a previous time (i.e. post-infall). 
    The decrease in the number of unique low-mass pairs from $z=2$ to $z=0$ is due to pairs being removed from the sample via mergers.\kc{change ylabel to "pairs"}
    }
    \label{fig:numorbits}
    \end{center}
\end{figure}

@@

% ###########################################################################################
% Results I
% ###########################################################################################
\begin{figure*}[htb]
    \begin{center}
    \includegraphics[width=0.7\textwidth]{plots/bet-on-it/3_Timevsseplow-2d.png}
    \caption{\kc{Add z=5, z=6 panels. Add colorbar for percentage per panel (and add number of pairs at that redshift) Add low/high label somewhere, is the lower sep set to 10kpc?} The distribution of times until merger for low-mass pairs as a function of physical separation at $z=0.5,1,1.5,2,3,\mbox{and }4$. 
    There is a positive correlation between separation at the selected redshift and the time until merger. 
    Of orbit-selected merging pairs at $z=1$, the majority are found with separations $\rsep<100\,\kpc$, and will merge within $3-4\, \Gyr$. 
    Merger times are longer for lower redshift pairs, and the distribution of separations is larger.
    The lowest separation pairs have the shortest merger timescales.
    This plot can be used to get estimates for the merger timescale of an isolated low-mass pair at a given redshift. For example, a low-mass pair at $z=2$ with $\rsep\sim 75\,\kpc$ will merge in $0-6\,\Gyr$, with a most likely time to merger of around $2\Gyr$.
    \kc{add z=5, z=6, add horizontal line for the time remaining in the sim in panel 1}
    }
    \label{fig:timevssep-low}
    \end{center}
\end{figure*}

>>>>

\section{Pair Sample Properties}
\begin{figure}[htb]
    \begin{center}
    \includegraphics[width=\columnwidth]{plots/bet-on-it/6_paircount.png}
    \caption{The number of low-mass (green) and high-mass (pink) unique pairs (or distinct orbits) that are post-infall and pre-merger as a function of redshift. 
    The solid lines show the total number of pairs at a given redshift (including non-mergers and mergers that have yet to merge), while dashed lines show the number of post-infall orbits at a given redshift that will merge before $z=0$.
    We only count the number of orbits ``at" a given redshift if they have not merged, but have experienced first infall at a previous time (i.e. post-infall). 
    The decrease in the number of unique low-mass pairs from $z=2$ to $z=0$ is due to pairs being removed from the sample via mergers.
    }
    \label{fig:numorbits}
    \end{center}
\end{figure}

@@

% ###########################################################################################
% Results I
% ###########################################################################################
\begin{figure*}[htb]
    \begin{center}
    \includegraphics[width=0.8\textwidth]{plots/bet-on-it/8_2Dhist.png}
    \caption{\kc{(and add number of pairs at that redshift?) Add low/high label somewhere, is the lower sep set to 10kpc?} The distribution of times until merger for low-mass pairs as a function of physical separation at $z=0.5,1,1.5,2,3,\mbox{and }4$. 
    There is a positive correlation between separation at the selected redshift and the time until merger. 
    Of orbit-selected merging pairs at $z=1$, the majority are found with separations $\rsep<100\,\kpc$, and will merge within $3-4\, \Gyr$. 
    Merger times are longer for lower redshift pairs, and the distribution of separations is larger.
    The lowest separation pairs have the shortest merger timescales.
    This plot can be used to get estimates for the merger timescale of an isolated low-mass pair at a given redshift. For example, a low-mass pair at $z=2$ with $\rsep\sim 75\,\kpc$ will merge in $0-6\,\Gyr$, with a most likely time to merger of around $2\Gyr$.
    \kc{add z=5, z=6, add horizontal line for the time remaining in the sim in panel 1}
    }
    \label{fig:timevssep-low}
    \end{center}
\end{figure*}
